---
title: "Introduction to drawmap"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Introduction to drawmap}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  dpi = 1200
)
```

```{r setup}
library(drawmap)
```

In this vignette, we will demonstrate how to draw a map of Norway and
surrounding countries with `drawmap::draw()`.

## Load data

### Load map data

Firstly, we load the map data for Norway and surrounding European countries with
`load_maps_data()`.

```{r load-map-data}
norway <- load_maps_data(countries = "Norway")
europe <- load_maps_data()
```

### Create a data frame with place names and coördinates

Secondly, we create a data frame with place names and their coördinates in WGS84
format. We will use this data frame to label the map with place names.^[Note
that the `Coordinates_WGS84` column contains the latitude and longitude of the
places separated by a comma. The data frame is constructed in this fashion also
to illustrate how to use and customise the `load_coordinates()` function.]

```{r coordinates}
places <- data.frame(
  Place = c(
    "Oslo",
    "Bergen",
    "Stavanger",
    "Trondheim",
    "Tromsø"
  ),
  Coordinates_WGS84 = c(
    "59.913333, 10.738889",
    "60.389444, 5.33",
    "58.97, 5.731389",
    "63.429722, 10.393333",
    "69.682778, 18.942778"
  )
)

coordinates <- load_coordinates(
  data = places,
  factor_cols = "Place",
  mutate_val = "Some of the major cities in Norway"
)
```

## Draw map of Norway and surrounding countries

Next, we draw the map using `drawmap::draw()`. We specify the area data for
Norway and the other European countries, as well as the colours for the areas
and borders. Here, we use the `sans` font for the map. The resulting map is
displayed below.^[Note that the graphics device backend was set to `AGG` in
RStudio when rendering this vignette to ensure that the custom font was
displayed correctly.] In addition, we add labels for some of the major cities in
Norway using the `coordinates` data frame.

```{r draw-map, fig.width = 5.68, fig.height = 6.50, out.width = "100%"}
#| fig.alt: >
#|   Map of Norway, with labels for some of the major cities, and surrounding
#|   countries.
p <- draw(
  area_data = norway,
  area_col = "#512888",
  area_fill = "#D4C2ED",
  other_areas_data = europe,
  other_areas_col = "#ADB0B8",
  other_areas_fill = "#D9DCE6",
  font = "sans",
  coordinates = coordinates,
  label_repel = TRUE
)

p
```
